---
title: "Assignment-3"
author: "Cahit Barkın Özer"
date: "09 01 2022"
output: word_document
---
****
### 1.Write a function that finds a prime number(s) given a set of numbers. Your function also provides prime factors of non-prime numbers. For example you have a vector of numbers like (89, 107, 597, 931, 1083). Your result will be Prime numbers : 89 107 Non-prime numbers : 597 [3 199]  931 [7 7 19] 1083 [3 19 19]
```{r include=FALSE}
library(tidyverse)
```
```{r}
flag = 0
is.prime <- function(prime_vector) {
  
  prime<-vector()
  non_prime<-vector()
  
  divider<-0
  for(x in prime_vector ){ #For every number in vector
    
    if(x > 1) {
      flag = 1
      for(i in 2:(x-1)) { # i from 2 to last number
        if ((x %% i) == 0) { #Check if i can divide number
          flag = 0           #Flag set to 0
          break
        }
      }
    } 
    if(x == 2){flag = 1}      #If number is 2, it is prime
    if(flag == 1) {           #If flag is 1, it is prime
      prime<-c(prime,x)       #Add to prime
    } else {                  #Else flag is 0
      
      non_prime<-c(non_prime,x)  #Add to non_prime. Now add it's prime factors
      
      #Least common diviser to find prime factors 
      if (x > 2) {
        prime_factor <- vector()
        while(x %% 2 == 0){
          prime_factor = c(prime_factor, 2)
          x = x/2
        }
        
        factor_count = 3
        while(x != 1) {
          while(x %% factor_count == 0) {
            prime_factor = c(prime_factor, factor_count)
            x = x/factor_count
          }
          factor_count = factor_count + 2
        }
      }
     
      non_prime<-c(non_prime,paste("[",prime_factor,"]")) #Add dividers 
      
    }
    
  }
  print(paste(c("Prime numbers:",prime,"\n Non-prime numbers:",non_prime), collapse=" "))
  }
```
```{r include=FALSE}
prime_vector<-c(89,107,597,931,1083)
result<- is.prime(prime_vector)
```
Result for the vector (89, 107, 597, 931, 1083): \
"`r result`"

### 2.Write a function that finds the letter numbers of all words in a given text and sorts the text according to those numbers from words with few letters to words with many letters. Sort the words containing the same number of letters alphabetically. For having text, you may use Sentences in tidyverse. Select 5 or 6 sentences randomly from Sentences.
```{r include=FALSE}
library(tidyverse)
library(stringr)
set.seed(2018556059)
sentence<-stringr::sentences
```

```{r}
a<-sample(1:2,1) #Flip a coin
a<-if_else(a==1,5,6) #If it is 1 a is 5 (if it is 2 a is 6)
main_sample <- sentence[sample(length(sentence), a)]#Sampling 5 or 6 sentences randomly
sample <- str_replace(main_sample, "\\.", "")  #Deleting "." in sentences.
sentence.sort<-function(x){
  my_words<-vector()
  temp_words<-vector()
  for (i in x) {                           #For every element in sentences
    temp_words <- str_split(x, " ")        #Add sentences in vector
    for (word in temp_words){              #For every word in sentences
      my_words <- c(my_words, word)        #Add word to my_words vector
    }
  }
  my_words<-unique(my_words)               #Remove duplication
  x<-my_words
  x<-tolower(x)                            #Lower the words
  sorted<-str_sort(x, locale="eng")        #Sort alphabetically
  sorted<-sorted[order(nchar(sorted), sorted)]
  return(paste(sorted, collapse = " "))    #Concatenate every word separated by " "
}
```
My sentences are: \
"`r main_sample`" \
\
My function return the result: \
"`r sentence.sort(sample)`"
