---
title: "Assignment-1"
author: "Cahit Barkın Özer"
date: "09 01 2022"
output: word_document
---
****
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) #Turning off R markdown warning and messages
```
```{r include=FALSE}
library(tidyverse)
library(knitr)
```
With using “starwars” tibble in dplyr package, please answer the following questions: \
1.How many characters do have at least one starship? List the names of the characters having at least one starship. \
```{r}
ship_owners<-filter(starwars,starships !="character(0)")
len<-length(ship_owners$name)
name<- ship_owners$name
```
"`r len`" characters have at least one ship. \
Names of the characters having at least one starship: \
"`r name`" \
\
2.Get the frequencies of the eye color of the characters. Rank them from most to least.
```{r echo=FALSE}
eye_frequency<-starwars %>%
  group_by(eye_color) %>%
  summarize(
    count=n()
  )
kable(arrange(eye_frequency,desc(count)))
```


3.According to the data available, what are the mean (average) age values across each species? \
Find the 3 oldest species. Note that in the data, there is no age column, instead there is a birth_year column. \
This column represents how many years before the Battle of Yavin the character was born. \
So take this column as the ages of characters at the Battle of Yavin and calculate the mean. \

```{r echo=FALSE}
#When an element of a specie's birth_year is null
#Mean becomes null therefore I deleted NA values

na_deleted=filter(starwars,birth_year !="NA")

mean_age<-na_deleted %>%
  group_by(species) %>%
  summarize(
    mean_birth=mean(birth_year)
  )

kable(mean_age)

specie_mean_age<-arrange(mean_age,desc(mean_birth))

kable(specie_mean_age[c(1,2,3),])
```


4.Create a new data set by adding a new observation to this data.\
This observation should be based on your own character (your name or nickname, your weight and height, your homeworld, your starships etc). \
Note that you can pick one or more than one Star Wars films in which you played as a movie star. \

```{r echo=FALSE}
my_character<-rbind(starwars,c(name="cbarkinozer",height=183,mass=70,
                               hair_color="brown",skin_color="light",
                               eye_color="blue",
                               birth_year=22.0,sex="male",gender="masculine",
                               homeworld="Tatooin",species="Human","A New Hope",
                               "Imperial speeder bike","x-wing"))

my_character$height<-as.integer(my_character$height)

my_character$mass<-as.double(my_character$mass)

kable(tail(my_character,1))
```
Result truncated to the last row.
\
5.Calculate the body mass index (BMI) values (dividing the mass value in kg to the square of the height value in meter) \
for all observations and categorize the observations as underweight (BMI below 18.5),\
healthy (BMI between 18.5-24.99), overweight (BMI between 25.0-29.99) and obese (BMI above 30.0).\
Add these two variables to your new data created at the 4th question. \
```{r echo=FALSE}
my_character<-my_character %>%
  mutate(my_character,BMI=mass/((height/100)^2))

my_character<-my_character %>%
  mutate(my_character,body_type=if_else(BMI<18.5,"underweight",
                                        if_else(BMI<25,"healthy",
                                                if_else(BMI<30,"overweight",
                                                        "obese"))))

kable(tail(my_character,1)) #Show the last row
```

6.Plot the distribution of ages less than 100 by BMI groups. (i.e. use filter function to select the ages less then 100) \
```{r echo=FALSE}
#NA body_types exist because some of their mass or height are NA.
#I didn't delete them because it gives us a clue that 
#those whose body_type is NA are over 50 years old.


my_character$birth_year<-as.integer(my_character$birth_year)

age_below_hundred<-filter(my_character,birth_year<100.0)

ggplot(data=age_below_hundred)+
  geom_point(mapping=aes(x=birth_year,y=body_type))

```

7.By plotting a graph, show the relationship between age and BMI values (use point and line at the same time). Re-plot the \ same graph after filtering the data as both age and BMI less than 100. \
```{r echo=FALSE}
ggplot(data=my_character)+
  geom_point(mapping=aes(x=birth_year,y=BMI))+
  geom_smooth(mapping=aes(x=birth_year,y=BMI))

ggplot(data=age_below_hundred,mapping=aes(x=birth_year,y=BMI))+
  geom_point()+
  geom_smooth(data=filter(age_below_hundred,birth_year<100 & BMI<100))
```
